
            \documentclass[../CaseBriefs.tex]{subfiles}
            \usepackage{lawbrief}
            \begin{document}
            \NewBrief{subject={Breach of Contract},
                    plaintiff={Beard Implement Co},
                    defendant={Krusa},
                    citation={208 Ill. App. 3d 953, 567 N.E.2d 345 (1991)},
                    course={Contracts},
                    facts={Defendant (Krusa) owned a farm with various pieces of farm equiptment. Defendant's combine broke down and he proceeded to buy a new one. Defendant went to plaintiff's (Beard Implement Co) to purchase a new combine and, after some negotiations, signed an order sheet to purchase the new combine for \$52,800 and the value of the defendant's current combine. The defendant had some misgivings, and left the plaintiff with the order sheet (not yet signed by plaintiff) and a check for a 10\% downpayment (not yet dated). After a couple of days, defendant found another dealer who offered a different combine for a lower price. He accepted, believing that since the check hadn't been dated and the contract hadn't been signed by plaintiff he was under no obligations. Plaintiff disagreed and sued for breach of contract.},
                    procedure={Trial Court: In favor of Plaintiff\\
Appeal: In favor of Defendant (Reversed)},
                    issue={In order for a contract to be inforcable, do all subsequent steps laid out in the contract need to be fulfilled?},
                    holding={Yes; Reversed},
                    principle={},
                    reasoning={No contract ever existed between defendant and plaintiff because plaintiff never accepted defendant's offer to purchase the combine because the purchase order defendant signed required a "dealer" signature on behalf of plaintiff which was not filled out.},
                    opinions={},
                    label={case:BeardVKrusa},
                    notes={}
            }
            \end{document}
        