
            \documentclass[../CaseBriefs.tex]{subfiles}
            \usepackage{lawbrief}
            \begin{document}
            \NewBrief{subject={Mutual Assent},
                    plaintiff={Lucy},
                    defendant={Zehmer},
                    citation={196 Va. 493, 84 S.E.2d 516 (1954)},
                    course={Contracts},
                    facts={The plantiffs W. O. Lucy and J. C. Lucy purchased a plot of land from defendants A. H. Zehmer and his wife in Dinwiddie county containing 471.6 acres of land for \$50,000.\\
The defendants drafted and signed the contract for the purchase stating "We hereby agree to sell to [plantiff] the Ferguson Farm complete for \$50,000.00, title satisfactory to buyer."\\
The defendants claim that they thought the offer was made in jest and, having had a few drinks, composed and signed the contract. Further, they claim that the plantiff was never delivered the contract and instead came by and picked it up and offered the defendant \$5 to bind the bargain. The defendant refused, at that point realizing for the first time that the offer was sincere. The plantiff left the property insisting that the purchase had been completed.\\
Seven or eight years earlier, plantiff had tried to purchase the farm from defendant for \$20,000 and defendant had verbally agreed, then backed out.\\
},
                    procedure={Trial Court: In favor of Defendant\\
Appeal: In favor of Plantiff (Reversed and remanded)},
                    issue={Can a written and signed contract be voided based on an internal and not obviously evident intention not to agree to the terms by one of the parties?},
                    holding={No; Reversed and remanded},
                    principle={An agreement between two persons is exclusively judged from the expressions of their intentions which are communicated between them.},
                    reasoning={An agreement or mutual assent is essential to a valid contract but the law imputes to a person the intention corresponding to the reasonable meaning of his words and acts. If his words and acts, judged by a reasonable standard, manifest an intention to agree, it is immaterial what may be the real but unexpressed state of his mind.},
                    opinions={},
                    label={case:LucyVZehmer},
                    notes={}
            }
            \end{document}
        